# 可视化 {#visualization}


Top 50 ggplot2 Visualizations - The Master List (With Full R Code)

http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html

https://data-se.netlify.com/2017/11/20/great-dataviz-examples-in-rstats/

Why I use ggplot2
http://varianceexplained.org/r/why-I-use-ggplot2/


## 空间数据可视化 {#sp-vis}

数据类型复杂，空间数据相关，地图

用 R 画中国地图并标注城市位置
https://yihui.name/cn/2008/10/china-map-and-city-locations-with-r/

无法重现但是用 base R 画地图的用法可以借鉴

Introduction to spatial analysis in R (rasters/sf) 

https://github.com/jafflerbach/spatial-analysis-R
https://jafflerbach.github.io/spatial-analysis-R/intro_spatial_data_R.html
https://jafflerbach.github.io/spatial-analysis-R/intro_to_sf.html

An Introduction to Spatial Econometrics in R
http://www.econ.uiuc.edu/~lab/workshop/Spatial_in_R.html
https://ignaciomsarmiento.github.io/2017/02/07/An-Introduction-to-Spatial-Econometrics-in-R

[Data wrangling visualisation and spatial analysis: R Workshop](https://www.seascapemodels.org/data/data-wrangling-spatial-course.html)


[sp-gallery]: https://edzer.github.io/sp/

- [Spatial Data in R: New Directions](https://edzer.github.io/UseR2017/) 
- [Mapping unemployment data](http://sharpsightlabs.com/blog/map-unemployment-nov-2016/)
- [Areal data. Lung cancer risk in Pennsylvania](https://paula-moraga.github.io/tutorial-areal-data/)
- [Geostatistical data. Malaria in The Gambia](https://paula-moraga.github.io/tutorial-geostatistical-data/)
- [GeoSpatial Data Visualization in R](https://bhaskarvk.github.io/user2017.geodataviz/)
- [Ecological Models and Data in R](http://ms.mcmaster.ca/~bolker/emdbook/)
- [Geographic Data Science in Python](https://data.cdrc.ac.uk/dataset/geographic-data-science-in-python)
- [Spatial](https://data.cdrc.ac.uk/)
- [Fast GeoSpatial Analysis in Python](http://matthewrocklin.com/blog/work/2017/09/21/accelerating-geopandas-1)
- [A gentle INLA tutorial](https://www.precision-analytics.ca/blog-1/inla)

- Reproducible road safety research: an exploration of the shifting spatial and temporal distribution of car-pedestrian crashes

https://github.com/Robinlovelace/stats19-gisruk

### raster 对象

星号 * 标记的是 S3 方法

```{r}
methods(plot)
```

查看函数的定义

```{r}
getAnywhere(plot.raster)
```

rasterImage 函数来绘制图像，如果想知道 `rasterImage` 的内容可以继续看 `getAnywhere(rasterImage)`

```{r}
getAnywhere(rasterImage)
```

通过查看函数的帮助 `?rasterImage` ，我们需要重点关注一下
参数 *image* 传递的 raster 对象

### sp 对象

空间数据对象，以类 sp 方式存储 [@Pebesma_2005_sp]

```{r,eval=FALSE}
library(sp)
data(meuse)
coords <- SpatialPoints(meuse[c("x", "y")])
meuse <- SpatialPointsDataFrame(coords, meuse)
plot(meuse, pch = 1, cex = .05 * sqrt(meuse$zinc))

library(maptools)
fname <- system.file("shapes/sids.shp", package = "maptools")
p4s <- CRS("+proj=longlat +datum=NAD27")
nc <- readShapePoly(fname, proj4string = p4s)
plot(nc, axes = TRUE, col = grey(1 - nc$SID79 / 57))

# Trellis maps

arrow <- list("SpatialPolygonsRescale",
  layout.north.arrow(2),
  offset = c(-76, 34), scale = 0.5, which = 2
)
spplot(nc, c("SID74", "SID79"),
  as.table = TRUE,
  scales = list(draw = T), sp.layout = arrow
)
```

::: warning
maptools 提供的 readShapePoly 函数去读取 shp 文件的方式已经过时，推荐使用 `rgdal::readOGR` 或者 `sf::st_read` 方式读取
:::

### sf 对象 {#simple-features}

- maps
- mapdata
- maptools
- mapproj

- rgeos
- rgdal

- sp
- sf





## 网络数据可视化 {#net-vis}

[igraph](https://igraph.org/) 提供了 R 和 Python 接口 <https://github.com/igraph>。

[qgraph](https://github.com/SachaEpskamp/qgraph) 开发者 [Sacha Epskamp](http://sachaepskamp.com) 在个人主页上提供了很多网络数据分析的学习资料


[Rgraphviz](https://www.bioconductor.org/packages/release/bioc/html/Rgraphviz.html) 基于 [Graphviz](https://www.graphviz.org/)

```{r,echo=TRUE,eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("Rgraphviz", version = "3.8")
```
