--- 
title: "R 语言绘图基础"
subtitle: "R Graphics Foundations"
author: "黄湘云"
date: "`r format(Sys.time(), tz = 'Asia/Taipei', usetz = TRUE)`"
site: bookdown::bookdown_site
documentclass: book
papersize: b5
linestretch: 1.25 # 1.25 倍行间距
#lof: yes
#lot: yes
#indent: 40pt # 段首缩进两个汉字
toccolor: magenta
fontsize: 10pt
secnumdepth: 2
colorlinks: yes
classoption: "UTF8,twoside"
bibliography: [latex/book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
subparagraph: true
geometry: [b5paper, tmargin=2.5cm, bmargin=2.5cm, lmargin=3.5cm, rmargin=2.5cm]
description: "R Graphics Foundations."
keywords: ["graphics", "grid", "lattice", "ggplot2"]
---

\mainmatter

# 准备 {#prerequisites}
\index{bookdown}
\index{knitr}
\index{pandoc}

[R图形]{.todo}

::: sidebar
You _can_ also create non-syntactic bindings using single or double quotes (e.g. `"_abc" <- 1`) instead of backticks, but you shouldn't, because you'll have to use a different syntax to retrieve the values. The ability to use strings on the left hand side of the assignment arrow is an historical artefact, used before R supported backticks.
:::

The **bookdown** package [@xie_2015_knitr] can be installed from CRAN or Github:

::: base
This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.
:::

```{r eval=FALSE,echo=TRUE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

## 为什么选择 R 语言

不管是在本科生还是研究生水平的教学中，R 语言都是帮助学习数理统计的[理想平台][why-r]

[why-r]: https://www.ejwagenmakers.com/misc/HortonEtAl2004.pdf

统计图形：

基本要素

点 pch cex 点的类型和大小  col 
线 lty lwd 线的类型和宽度  col 

颜色 col 连续型和离散型
面/多边形 rect 颜色填充

- 散点图
- 气泡图
- 条形图
- 直方图
- 折线图
- 时序图
- 饼图
- 箱线图
- 茎叶图
- 抖动图



强调图对应的数据类型

raster/sf https://github.com/jafflerbach/spatial-analysis-R

https://jafflerbach.github.io/spatial-analysis-R/intro_spatial_data_R.html
https://jafflerbach.github.io/spatial-analysis-R/intro_to_sf.html




## 软件信息 {#softwares-rsession-info}

```{r sessioninfo,echo=TRUE}
xfun::session_info(packages = c(
  "colorspace", "tikzDevice",
  "bookdown", "rmarkdown"
))
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
