--- 
title: "R 语言绘图基础"
subtitle: "R Graphics (foundation)"
author: "黄湘云"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
papersize: b5
linestretch: 1.25
lof: yes
lot: yes
fontsize: 10pt
colorlinks: yes
classoption: "UTF8,oneside"
bibliography: [latex/book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
subparagraph: true
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

\mainmatter

# 准备 {#prerequisites}

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package [@xie_2015_knitr] can be installed from CRAN or Github:

```{r eval=FALSE,echo=TRUE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r sessioninfo,echo=TRUE}
xfun::session_info(packages = c(
  "bookdown", "rmarkdown"
))
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
