--- 
title: "R 语言绘图基础"
subtitle: "R Graphics Foundations"
author: "黄湘云"
date: "`r format(Sys.time(), tz = 'Asia/Taipei', usetz = TRUE)`"
site: bookdown::bookdown_site
documentclass: book
papersize: b5
linestretch: 1.25 # 1.25 倍行间距
#lof: yes
#lot: yes
#indent: 40pt # 段首缩进两个汉字
toccolor: magenta
fontsize: 10pt
secnumdepth: 2
colorlinks: yes
classoption: "UTF8,twoside"
bibliography: [latex/book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
subparagraph: true
compact-title: true
geometry: [b5paper, tmargin=2.5cm, bmargin=2.5cm, lmargin=3.5cm, rmargin=2.5cm]
description: "R Graphics Foundations. 学习 R Base Graphics 部分的测试代码，函数各参数含义的查询手册，主要目的是帮助读者读懂参考手册，写作过程分步走：学习知识，记笔记，可写本书上或博客上，博客侧重在某个点的内容扩展上，书籍需要照顾覆盖面，各部分平衡一点，整理心得，再次修改笔记以符合书籍。所有的案例都基于真实数据集，基础R打包的数据集都是真实的，扩展案例就是在规模上进行扩展，选用基础R中的数据，原因是收集清洗真实数据是比较麻烦和费时间的事情"
keywords: ["graphics", "grid", "lattice", "ggplot2"]
---

\mainmatter

# 准备 {#prerequisites}
\index{bookdown}
\index{knitr}
\index{pandoc}

[R图形]{.todo}

::: sidebar
You _can_ also create non-syntactic bindings using single or double quotes (e.g. `"_abc" <- 1`) instead of backticks, but you shouldn't, because you'll have to use a different syntax to retrieve the values. The ability to use strings on the left hand side of the assignment arrow is an historical artefact, used before R supported backticks.
:::



The **bookdown** package [@xie_2015_knitr] can be installed from CRAN or Github:

::: base
This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.
:::

```{r eval=FALSE,echo=TRUE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

## 为什么选择 R 语言

不管是在本科生还是研究生水平的教学中，R 语言都是帮助学习数理统计的[理想平台][why-r]

[why-r]: https://www.ejwagenmakers.com/misc/HortonEtAl2004.pdf





## 软件信息 {#softwares-rsession-info}

编译本书需要的环境

```{r sessioninfo,echo=TRUE}
xfun::session_info(packages = c(
  "colorspace", 
  "bookdown", "rmarkdown"
))
```

重现本书内容需要的 R 包

```{r,eval=FALSE}
xfun::session_info(packages = c(
  "colorspace",
  "bookdown", "rmarkdown",
  "tikzDevice", "fontcm"
))
```
```
R version 3.5.2 (2018-12-20)
Platform: x86_64-w64-mingw32/x64 (64-bit)
Running under: Windows 8.1 x64 (build 9600)

Locale:
  LC_COLLATE=Chinese (Simplified)_China.936 
  LC_CTYPE=Chinese (Simplified)_China.936   
  LC_MONETARY=Chinese (Simplified)_China.936
  LC_NUMERIC=C                              
  LC_TIME=Chinese (Simplified)_China.936    

Package version:
  base64enc_0.1.3  bookdown_0.9     colorspace_1.4.0 digest_0.6.18   
  evaluate_0.12    filehash_2.4.1   fontcm_1.1       glue_1.3.0      
  graphics_3.5.2   grDevices_3.5.2  highr_0.7        htmltools_0.3.6 
  jsonlite_1.6     knitr_1.21       magrittr_1.5     markdown_0.9    
  methods_3.5.2    mime_0.6         png_0.1.7        Rcpp_1.0.0      
  rmarkdown_1.11   stats_3.5.2      stringi_1.2.4    stringr_1.3.1   
  tikzDevice_0.12  tinytex_0.9      tools_3.5.2      utils_3.5.2     
  xfun_0.4         yaml_2.2.0      

Pandoc version: 2.5
```

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
